---
title: "Statistical inference project 2"
author: "YOUNGSANG KIM"
output:
  pdf_document: default
  html_document:
    df_print: paged
editor_options:
  chunk_output_type: console
---
### EDA
```{r data}
library(dplyr, warn.conflicts = F)
library(ggplot2)
data("ToothGrowth")
summary(ToothGrowth)
str(ToothGrowth)
ToothGrowth$dose<-as.factor(ToothGrowth$dose) # Convert dose to a factor
```  


Plot tooth length ('len') vs. the dose amount ('dose'), broken out by supplement delivery method ('supp')
```{r plot, fig.height = 2, fig.width = 5}
ggplot(aes(x=dose, y=len), data=ToothGrowth) + geom_boxplot(aes(fill=dose)) +
  xlab("Dose Amount") + ylab("Tooth Length") + facet_grid(~ supp)
```  


Plot tooth length ('len') vs. supplement delivery method ('supp') broken out by the dose amount ('dose')
```{r, fig.height = 2 , fig.width = 5}
ggplot(aes(x=supp, y=len), data=ToothGrowth) + geom_boxplot(aes(fill=supp)) +
  xlab("Supplement Delivery") + ylab("Tooth Length") + facet_grid(~ dose)
```


### Hypothesis Tests  
Now we want to further compare teeth growth by supplement type and dose levels.  
This time we'll use statistical tests, t-test.
```{r}
len_1 <- ToothGrowth %>% filter(dose %in% c(0.5,1)) %>% select(len) %>% unlist()
dose_1 <- ToothGrowth %>% filter(dose %in% c(0.5,1)) %>% select(dose) %>% unlist()
t.test(len_1 ~ dose_1, paired = FALSE)
```
```{r}
len_2 <- ToothGrowth %>% filter(dose %in% c(0.5,2)) %>% select(len) %>% unlist()
dose_2 <- ToothGrowth %>% filter(dose %in% c(0.5, 2)) %>% select(dose) %>% unlist()
t.test(len_2 ~ dose_2, paired = FALSE)
```
```{r}
len_3 <- ToothGrowth %>% filter(dose %in% c(1,2)) %>% select(len) %>% unlist()
dose_3 <- ToothGrowth %>% filter(dose %in% c(1,2)) %>% select(dose) %>% unlist()
t.test(len_3 ~ dose_3, paired = FALSE)
```
We went through all possible combinations of levels.  
Thus, we reject Ho. In other words there appears to be a positive relationship between dose level and teeth length  
```{r}
len <- ToothGrowth %>% select(len) %>% unlist()
supp <- ToothGrowth %>% select(supp) %>% unlist()
t.test(len~supp, paired=F)
```
The p-value is 0.06, and the confidence interval contains zero.  
This indicates that we can not reject the null hypothesis that the different supplement types have no effect on tooth length.  


### Conclusions  
A. Increasing the dose level leads to increased tooth growth.  
B. Supplement type has no effect on tooth growth.  
Given the following assumption:  
A. The sample is representative of the population.  
B. The distribution of the sample means follows the Central Limit Theorem.
